---
title: "Project_Map"
author: "Sonisa Sharma"
date: "August 28, 2019"
output:
  ioslides_presentation: default
  slidy_presentation: default
  beamer_presentation: default
---
## Introduction

Leaflet is one of the most popular Javascript libraries for
creating interactive maps. The leaflet R package allows you
to create your own leaflet maps without needing to know any
Javascript!


*Get the Map of the world*


```{r, eval=FALSE}
library(leaflet)
library(dplyr)
my_map <- leaflet() %>% 
  addTiles()
my_map
```


## Adding Markers

**Here is the coding using leaflet and the output map showing the hospital and its size in Kathmandu, Nepal**


You can add markers to your map one at a time using the
`addMarkers()` function by specifying the longitude and
latitude. ([Here's](https://twitter.com/drob/status/719927537330040832)
a tip if you tend to mix them up.) You can specify popup
text for when you click on the marker with the `popup` 
argument.

```{r, eval=FALSE}
library(leaflet)
my_map <- my_map %>%
  addMarkers(lat=27.69, lng=85.2897, 
             popup="Hospital in Nepal")
my_map
```


## Adding Many Markers

Adding one marker at a time is often not practical if you
want to display many markers. If you have a data frame with
columns `lat` and `lng` you can pipe that data frame into
`leaflet()` to add all the points at once.

```{r, eval=FALSE}
set.seed(2016-04-25)
df <- data.frame(lat = runif(20, min = 27.71, max = 27.74),
                 lng = runif(20, min = 85.28, max = 85.38))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers()
```


## Drawing Circles

You can draw arbitrary shapes on the maps you create,
including circles and squares. The code below draws a map
where the circle on each city is proportional to the
population of that city.

```{r, eval=FALSE}
md_hospital <- data.frame(name = c("Hosp1", "Hosp2", "Hosp3", "Hosp4","Hosp5", "Hosp6","Hosp7", "Hosp8"),
                       pop = c(6194, 6616, 6233, 6104, 5523,
                                3989, 3888, 3058),
                        lat = c(27.693593,27.711681, 27.7525119,27.731705, 27.735186,27.734228,27.746302,27.749176),
                        lng = c(85.289752, 85.290593,85.295979,85.326538,85.328524,85.346133,85.344040,85.345918))
md_hospital %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = sqrt(md_hospital$pop) * 10)
```

## Drawing Rectangles

You can add rectangles on leaflet maps as well:

```{r, eval=FALSE}
leaflet() %>%
  addTiles() %>%
  addRectangles(lat1 = 27.711681, lng1 = 85.290993, 
                lat2 =27.749176, lng2 = 85.345918)
```

## Adding Legends

```{r, eval=FALSE}
df <- data.frame(lat = runif(20, min = 27.71, max = 27.74),
                 lng = runif(20, min = 85.28, max = 85.38),
                 col = sample(c("red", "blue", "green"), 20, replace = TRUE),
                 stringsAsFactors = FALSE)
df%>%
  leaflet()%>%
  addTiles()%>%
  addCircleMarkers(color = df$col) %>%
  addLegend(labels = LETTERS[1:3], colors = c("blue", "red", "green"))
```

## Conclusion

Thus, we were able to map the hopsital with the different size.